Measuring Individual Partisan Harm in Redistricting

### 2021-09-07 paper/paper.Rmd
legal cites better

---
title: Measuring Individual Partisan Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: Footnote stuff
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - individual standing
bibliography: references.bib
biblio-style: apalike
output: 
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
---

@@

The notion of district *competitiveness*, while related to the slope of the seats-vote curve around $\half$, is not the same as partisan symmetry.
However, one commonly used measure of competitiveness, from @tamcho2016, is related to our local utility measure $U^{(L)}$.
The measure of @tamcho2016, which we will denote by $\mathrm{comp}_\alpha(v,q)$ contains two terms: one, $T_p(v,q)$, measuring the closeness of district vote shares to 50%, and the other, $T_e(v,q)$, measuring the closeness of the overall share of seats to 50%; the relative importance of these two terms is controlled by $\alpha$.
It is this first term which his closely related to $U^{(L)}$, as stated in Proposition \ref{prop:comp} below.

@@

@@

\begin{proof}
\end{proof}
```

>>>>

---
title: Measuring Individual Partisan Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: Footnote stuff
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - individual standing
citation_package: biblatex
bibliography: references.bib
biblio-style: apa
output: 
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
---

@@

The notion of district *competitiveness*, while related to the slope of the seats-vote curve around $\half$, is not the same as partisan symmetry.
However, one commonly used measure of competitiveness, from @tamcho2016, is related to our local utility measure $U^{(L)}$.
The measure of @tamcho2016, which we will denote by $\mathrm{comp}_\alpha(v,q)$, contains two terms: one, $T_p(v,q)$, measuring the closeness of district vote shares to 50%, and the other, $T_e(v,q)$, measuring the closeness of the overall share of seats to 50%; the relative importance of these two terms is controlled by $\alpha$.
It is this first term which his closely related to $U^{(L)}$, as stated in Proposition \ref{prop:comp} below.

@@

# References {.unnumbered}

::: {#refs}
:::

\clearpage

@@

\begin{proof}
\end{proof}
```
# Computing Utility, Harm, and Fairness from Precinct-level Election Data

formulas here.
